\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-12-20 archive.tex
improvements to figures

\begin{figure}
  \begin{tikzpicture}[line width=0.4mm]
    \draw[fill=teal!5!white] (-1,1) -- (13,1) -- (13,-4) -- (-1,-4) -- (-1,1);
    \node at (5.5,1.25) {\textsc{\textbf{Wake}}};

@@

    \node at (0.5,-4.75) {\textbf{\textsc{Sleep: Consolidation}}};
    \draw[fill=teal!5!white] (-2,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-2,-13) -- (-2,-5);
    \node at (11.5,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw[fill=teal!5!white] (14,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (14,-13) -- (14,-5);

@@

    %%}b memory consolidation
    \begin{scope}[shift={(-2,-4.5)}]
      \node[align=center] at (0.8,-1.2) (f1){progs. for\\task$_1$:\\\mcode{(+ (car z) 1)}};
      \node[align=center] at ([xshift = 1cm]f1.east) (f2){progs. for\\task$_2$:\\\mcode{(cons (+ 1 1))}};
      \node[align=center] at ([yshift = 0cm,xshift=0.4cm]f2.east) (f3){\textbf{DSL}\\\mcode{cons}, \mcode{+}, \\...};
      \node(c)[rectangle, rounded corners, dashed, draw, minimum width = 3.75cm, minimum height = 3cm, anchor = north] at ([yshift=-0.8cm,xshift=-0.3cm]f2.south) {};
      \draw [-> ] (f1.south) -- (f1.south|-c.north);
      \draw [-> ] (f2.south) -- (f2.south|-c.north);
      \draw [-> ] (f3.south) -- (f3.south|-c.north);

      \node(d) at ([yshift = -1.8cm]c.south) {
        \begin{tikzpicture}[scale=0.9,line width=0.5mm]
          \node[align=center] at (0,0) {DSL w/ \code{(+ x 1)}:};
          \begin{scope}[shift={(0.6,-0.5)}]
            \node[pop3](p1) at (-1,-1) {\code{+}};
            \node[pop3](n1) at (0.6,-0.9) {\code{1}};
            \node[pop3](a) at (0,-1) {\code{ }};
            \draw[pop3] (0,0) -- (p1.north);
            \draw[pop3] (0,0) -- (n1.north);
            \draw[pop3] (-0.3,-0.3) -- (a.north);
          \end{scope}
      \end{tikzpicture}};
      \draw [-> ] (c.south) -- (d.north);

@@

          \begin{scope}[shift={(1,2)}]
            \node(l1) at (0,0) {};
            \node[color=pop3](p1) at (-1,-1) {\code{+}};
            \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
            %\node(x1) at (0,-1) {};
            \draw[color=pop3] (l1.south) -- (p1.north);
            \draw[color=pop3] (l1.south) -- (n1.north);
            \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

@@

%    \draw (0,0) rectangle (10,5);
    \node(t1)[align=left] at (1,-1) {
      \footnotesize +106 769-43$\to $106.769.43\\
      \footnotesize +83 973-831$\to $83.973.831\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(}\subnode{f01}{${\color{\inventionColor}f_0}$}\mcode{  \codechar{.} \codechar{-}}\\
      \footnotesize \hspace{1.25cm}\mcode{(${\color{\inventionColor}f_0}$ \codechar{.} \codechar{ }}\\
      \footnotesize \hspace{1.4cm}\mcode{(cdr s)))}
    };
    \node(t2)[align=left] at ([xshift=2cm]t1.east) {
      \footnotesize Dream Coder$\to$Dr. Dream\\
      \footnotesize Andy Cencici$\to$Dr. Andy\\
      \footnotesize Jan Kotas$\to$Dr. Jan\\
      \footnotesize Nancy Jones$\to$Dr. Nancy\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(${\color{\inventionColor}f_3}$ (${\color{\inventionColor}f_4}$ \codechar{ } s))}
    };
    \node(t3)[align=left] at ([xshift=2cm]t2.east) {
      \footnotesize Dream (Coder)$\to$Coder\\
      \footnotesize 1 (2) 3 4$\to$2\\
      \footnotesize the (dog) ran$\to$ran\\
      \footnotesize +817(33)99$\to$33\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(${\color{\inventionColor}f_6}$ \codechar{(} \codechar{)} s)}
    };

@@

    \renewcommand{\horizontalSpacing}{3.5cm}
    \renewcommand{\verticalSpacing}{2cm}

@@

    \begin{scope}[shift={(0,-15)}]
      \invention{filter}{0,0}{
        ${\color{\inventionColor}f_0} = $\mcode{($\lambda$ (p l)\\ (fold ($\lambda$ (x a)\\ (if (p x) (cons x a) a))\\ nil l))} 
        }{higher-order `filter'}

      \invention{three}{[yshift=-\verticalSpacing]filter.center}{\footnotesize ${\color{\inventionColor}f_1} = $\\\mcode{(+ 1 (+ 1 1))}}{The number `3'}
      \invention{prefix}{[yshift=-\verticalSpacing]three.center}{\footnotesize ${\color{\inventionColor}f_2} = $\mcode{($\lambda$ (n l) (map ($\lambda$ (i) (index i l)) (range (+ 1 n))))}}{First $n$ elements}
      \invention{single}{[xshift=\horizontalSpacing]filter.center}{\footnotesize ${\color{\inventionColor}f_3} = $\mcode{($\lambda$ (z l) (fold ($\lambda$ (x y) (cons x y)) z l))}}{Append element}
      \invention{for}{[yshift=-\verticalSpacing]single.center}{\footnotesize ${\color{\inventionColor}f_4} = $\mcode{(+ 1 ${\color{\inventionColor}f_1}$)}}{The number `4'}
      \invention{Max}{[yshift=-\verticalSpacing]for.center}{\footnotesize ${\color{\inventionColor}f_5} = $\mcode{($\lambda$ (l) %
          (car (${\color{\inventionColor}f_0}$ ($\lambda$ (x) (nil? (${\color{\inventionColor}f_0}$ l ($\lambda$ (z) (> z x))))) l)))}}{Max of list}
      \invention{largest}{[xshift=\horizontalSpacing]single.center}{\footnotesize ${\color{\inventionColor}f_6} = $\mcode{($\lambda$ (l n) %
          (${\color{\inventionColor}f_5}$ (${\color{\inventionColor}f_0}$ ($\lambda$ (x) (> n (length (${\color{\inventionColor}f_0}$ ($\lambda$ (y) (> x y)) l)))) l)))}}{$n^{\text{th}}$ largest element}
      \vinvention{count}{largest}{\footnotesize ${\color{\inventionColor}f_7} = $\mcode{($\lambda$ (x l) %
          (length (${\color{\inventionColor}f_0}$ ($\lambda$ (y) (= x y)) l)))}}{count}
      \vinvention{weird}{count}{\footnotesize ${\color{\inventionColor}f_8} = $\mcode{($\lambda$ (p l) %
          (map ($\lambda$ (x) (if (p x) (+ 1 x) 0))))}}
                 {Higher-order incrementer}

@@

      \node(t1)[align=left] at (0,3) {
        \mcode{[1 4 5 8]$\to$[5 8]}\\
        \mcode{[9 8 3 8]$\to$[9 8 8]}\\
        \mcode{[3 4 5 6]$\to$[5 6]}\\
        \mcode{[6 5 4 3]$\to$[6 5]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(${\color{\inventionColor}f_0}$ ($\lambda$ (x)}\\\hspace{0.5cm}\mcode{ (> x ${\color{\inventionColor}f_4}$)) z)}
      };
      \node(t2)[align=left] at ([xshift=3.75cm]t1.center) {
        \mcode{[9 2 4]$\to$[4 2 9]}\\
        \mcode{[4 3]$\to$[3 4]}\\
        \mcode{[3 4 5 6]$\to$[6 5 4 3]}\\
        \mcode{[]$\to$[]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(fold ($\lambda$ (x a)}\\\hspace{0.25cm}\mcode{ (${\color{\inventionColor}f_3}$ x a)) nil z)}
      };
      \node(t3)[align=left] at ([xshift=3.75cm]t2.center) {
        \mcode{[9 2 3]$\to$[2 3 9]}\\
        \mcode{[2 1]$\to$[1 2]}\\
        \mcode{[8 7 9 2 5]$\to$[2 5 7 8 9]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(map ($\lambda$ (i)}\\\hspace{0.5cm}\mcode{ (${\color{\inventionColor}f_6}$ z i)) }\\\hspace{0.5cm}\mcode{(+ 1 (range (length z)))}
      };

      \draw[->] ([yshift=0.5cm,xshift=-0.2cm]t1.south) to[out=250] (filter.north);
      \draw[->] ([yshift=0.0cm,xshift=0.3cm]t1.south) to[out=350,in=100] (for.west);
      \draw[->] ([xshift=-0.7cm]t2.south) -- (single.north);
      \draw[->] ([xshift=-1.25cm,yshift=0.5cm]t3.south) to[out=240] (largest.north);

@@

>>>>

\begin{figure}
  \begin{tikzpicture}[line width=0.4mm]
    \draw[fill=white!5!white] (-1,1) -- (13,1) -- (13,-4) -- (-1,-4) -- (-1,1);
    \node at (5.5,1.25) {\textsc{\textbf{Wake}}};

@@

    \node at (0.5,-4.75) {\textbf{\textsc{Sleep: Consolidation}}};
    \draw[fill=white!5!white] (-2,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-2,-13) -- (-2,-5);
    \node at (11.5,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw[fill=white!5!white] (14,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (14,-13) -- (14,-5);

@@

    %%}b memory consolidation
    \begin{scope}[shift={(-1.9,-4.5)}]
      \node[align=center] at (0.8,-1.2) (f1){progs. for\\task$_1$:\\%
        \mcode{(+ (car z)}\vspace{-5pt}\\\mcode{1)  }};
      \node[align=center] at ([xshift = 0.7cm]f1.east) (f2){progs. for\\task$_2$:\\\mcode{(cons }\vspace{-5pt}\\\mcode{(+ 1 1))}};
      \node[align=center] at ([xshift=0.7cm]f2.east) (f3){\textbf{DSL}\\\mcode{cons}, \mcode{+}, \\...};
      \node(c)[rectangle, rounded corners, dashed, draw, minimum width = 3.75cm, minimum height = 3cm, anchor = north] at ([yshift=-0.8cm,xshift=-0.0cm]f2.south) {};
      \draw [-> ] (f1.south) -- (f1.south|-c.north);
      \draw [-> ] (f2.south) -- (f2.south|-c.north);
      \draw [-> ] (f3.south) -- (f3.south|-c.north);

      \node(d) at ([yshift = -1.8cm]c.south) {
        \begin{tikzpicture}[scale=0.9,line width=0.5mm]
          \node[align=center] at (0,0) {\textbf{new DSL} w/ \texttt{(+ x 1)}:};
          \begin{scope}[shift={(0.6,-0.5)}]
            \node[pop3](p1) at (-1,-1) {\texttt{+}};
            \node[pop3](n1) at (0.6,-0.9) {\texttt{1}};
            \node[pop3](a) at (0,-1) {\texttt{ }};
            \draw[pop3] (0,0) -- (p1.north);
            \draw[pop3] (0,0) -- (n1.north);
            \draw[pop3] (-0.3,-0.3) -- (a.north);
          \end{scope}
      \end{tikzpicture}};
      \draw [-> ] (c.south) -- (d.north);

@@

          \node(l1) at (0,0) {};
          \node[color=pop3](p1) at (-1,-1) {\texttt{+}};
          \node[color=pop3](n1) at (0.7,-0.9) {\texttt{1}};
          \node(x1) at (0,-1) {\texttt{1}};
          \draw[color=pop3] (l1.south) -- (p1.north);
          \draw[color=pop3] (l1.south) -- (n1.north);
          \draw[color=pop3] (-0.5,-0.45) -- (x1.north);

          \node(t) at (-0.5,0.5) {};
          \draw (l1.south) -- (t.south);
          \node(c) at (-1.5,-0.2) {\texttt{cons}};
          \draw (t.south) -- (c.north);

          \begin{scope}[shift={(1,2)}]
            \node(l1) at (0,0) {};
            \node[color=pop3](p1) at (-1,-1) {\texttt{+}};
            \node[color=pop3](n1) at (0.7,-0.9) {\texttt{1}};
            %\node(x1) at (0,-1) {};
            \draw[color=pop3] (l1.south) -- (p1.north);
            \draw[color=pop3] (l1.south) -- (n1.north);
            \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

            \node(c) at (-0.5,-1.5) {\texttt{car}};
            \node(z) at (0.5,-1.5) {\texttt{z}};

@@

\begin{figure}
  \begin{tikzpicture}
    \renewcommand{\baselinestretch}{0.5}
    \renewcommand{\inventionColor}{orange}
    \newcommand{\name}[2]{
      \mcode{{\color{\inventionColor}$f_{#1}$}$($#2$)\,=\,$}
    }
    \newcommand{\noArguments}[1]{
      \mcode{{\color{\inventionColor}$f_{#1}\,=\,$}}
    }

    \renewcommand{\horizontalSpacing}{3.8cm}
    \renewcommand{\verticalSpacing}{2cm}

%    \draw (0,0) rectangle (10,5);
    \node(t1)[align=left] at (1,-1) {
      \footnotesize +106 769-43$\to $106.769.43\\
      \footnotesize +83 973-831$\to $83.973.831\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(}\subnode{f01}{${\color{\inventionColor}f_0}$}\mcode{  \codechar{.} \codechar{-}}\\
      \footnotesize \hspace{1.25cm}\mcode{(${\color{\inventionColor}f_0}$ \codechar{.} \codechar{ }}\\
      \footnotesize \hspace{1.4cm}\mcode{(cdr s)))}
    };
    \node(t2)[align=left,anchor=center] at ([xshift=\horizontalSpacing]t1.center) {
      \footnotesize Dream Coder$\to$Dr. Dream\\
      \footnotesize Andy Cencici$\to$Dr. Andy\\
      \footnotesize Jan Kotas$\to$Dr. Jan\\
      \footnotesize Nancy Jones$\to$Dr. Nancy\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(${\color{\inventionColor}f_3}$ (${\color{\inventionColor}f_4}$ \codechar{ } s))}
    };
    \node(t3)[align=left] at ([xshift=2cm]t2.east) {
      \footnotesize Dream (Coder)$\to$Coder\\
      \footnotesize 1 (2) 3 4$\to$2\\
      \footnotesize the (dog) ran$\to$ran\\
      \footnotesize +817(33)99$\to$33\\
      \footnotesize $f(\text{\mcode{s}}) = $\mcode{(${\color{\inventionColor}f_6}$ \codechar{(} \codechar{)} s)}
    };

@@

@@

    \begin{scope}[shift={(0,-15)}]
      \invention{filter}{0,0}{
        \name{0}{p$,$z}\mcode{\\(fold ($\lambda$ (x a)\\ (if (p x) (cons x a) a))\\ nil z)} 
        }{higher-order `filter'}

      \vinvention{three}{filter}{\footnotesize ${\color{\inventionColor}f_1} = $\\\mcode{(+ 1 (+ 1 1))}}{The number `3'}
      \vinvention{prefix}{three}{\name{2}{n$,$z}\\\mcode{(map ($\lambda$ (i) (index i z)) (range (+ 1 n)))}}{First $n$ elements}
      \hinvention{single}{filter}{\name{3}{z$,$l}\\\mcode{(fold ($\lambda$ (x y)\\(cons x y))\\ z l)}}{Append element}
      \vinvention{for}{single}{\footnotesize ${\color{\inventionColor}f_4} = $\mcode{(+ 1 ${\color{\inventionColor}f_1}$)}}{The number `4'}
      \vinvention{Max}{for}{\name{5}{l}\\\mcode{%
          (car (${\color{\inventionColor}f_0}$ ($\lambda$ (x) (nil? (${\color{\inventionColor}f_0}$ l ($\lambda$ (z) (> z x))))) l))}}{max of list}
      \hinvention{largest}{single}{\name{6}{l$,$n}\\\mcode{(${\color{\inventionColor}f_5}$ (${\color{\inventionColor}f_0}$ ($\lambda$ (x) \\(> n (length (${\color{\inventionColor}f_0}$ ($\lambda$ (y) (> x y)) l)))) l))}}{$n^{\text{th}}$ largest element}
      \vinvention{count}{largest}{\name{7}{p$,$l}\\\mcode{(length\\ (${\color{\inventionColor}f_0}$ ($\lambda$ (y) (= x y)) l))}}{count}
      \vinvention{weird}{count}{\name{8}{p$,$l}\mcode{
          (map ($\lambda$ (x) (if (p x) (+ 1 x) 0))))}}
                 {Higher-order incrementer}

@@

      \node(t1)[align=left,anchor=center] at (0,3) {
        \mcode{[1 4 5 8]$\to$[5 8]}\\
        \mcode{[9 8 3 8]$\to$[9 8 8]}\\
        \mcode{[3 4 5 6]$\to$[5 6]}\\
        \mcode{[6 5 4 3]$\to$[6 5]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(${\color{\inventionColor}f_0}$ ($\lambda$ (x)}\\\hspace{0.5cm}\mcode{ (> x ${\color{\inventionColor}f_4}$)) z)}
      };
      \node(t2)[align=left] at ([xshift=\horizontalSpacing]t1.center) {
        \mcode{[9 2 4]$\to$[4 2 9]}\\
        \mcode{[4 3]$\to$[3 4]}\\
        \mcode{[3 4 5 6]$\to$[6 5 4 3]}\\
        \mcode{[]$\to$[]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(fold ($\lambda$ (x a)}\\\hspace{0.25cm}\mcode{ (${\color{\inventionColor}f_3}$ x a)) nil z)}
      };
      \node(t3)[align=left] at ([xshift=\horizontalSpacing]t2.center) {
        \mcode{[9 2 3]$\to$[2 3 9]}\\
        \mcode{[2 1]$\to$[1 2]}\\
        \mcode{[8 7 9 2 5]$\to$[2 5 7 8 9]}\\
        \footnotesize $f(\text{\mcode{z}}) = $\mcode{(map ($\lambda$ (i)}\\\hspace{0.5cm}\mcode{(${\color{\inventionColor}f_6}$ z i)) }\\\hspace{0.5cm}\mcode{(+ 1 (range }\\\hspace{0.5cm}\mcode{(length z)))}
      };

      \draw[->] ([yshift=0.35cm,xshift=-0.3cm]t1.south) to[out=250] (filter.north);
      \draw[->] ([yshift=0.0cm,xshift=0.3cm]t1.south) to[out=350,in=100] (for.west);
      \draw[->] ([xshift=-0.7cm]t2.south) -- (single.north);
      \draw[->] ([xshift=-1.3cm,yshift=0.6cm]t3.south) to[out=240] (largest.north);

@@

    \newcommand{\name}[2]{
      \mcode{{\color{\inventionColor}$f_{#1}$}$($#2$)\,=\,$}
    }
    \newcommand{\noArguments}[1]{
      \mcode{{\color{\inventionColor}$f_{#1}\,=\,$}}
    }
    \newcommand{\use}[1]{{\color{\inventionColor}$f_{#1}$}}
    \renewcommand{\horizontalSpacing}{3.9cm}
    \renewcommand{\verticalSpacing}{2cm}

    \newcommand{\invention}[4]{
      \node(#1)[inner sep=1,anchor=south,text width=2cm,draw,rounded corners,align=center] at (#2) {
        \footnotesize #3
      };
      \node[anchor=north,align=center] at ([yshift=3.5pt]#1.south) {#4};
    }
    \newcommand{\vinvention}[4]{
      \invention{#1}{[yshift=-\verticalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\hinvention}[4]{
      \invention{#1}{[xshift=\horizontalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\exampleFunction}[2]{
      \includegraphics[width = 0.5cm]{#1}, \includegraphics[width = 0.5cm]{#2}
    }
    \node[anchor=center,align=center](t1) at (2,0) {
      \includegraphics[width = 2cm]{figures/logoTasks/logo144.png}\\
    \mcode{(for (i 4) (\use{3} i))}};
    \node[anchor=center,align=center](t2) at ([xshift=\horizontalSpacing]t1.center) {
      \includegraphics[width = 2cm]{figures/logoTasks/logo121.png}\\
    \mcode{(\use{7} 6 (\use{1} \use{0}))}};
    \node[anchor=center,align=center](t3) at ([xshift=\horizontalSpacing]t2.center) {
      \includegraphics[width = 2cm]{figures/logoTasks/logo133.png}\\
      \mcode{(\use{7} 7 (\use{8} \use{6}))}};
    \invention{circle}{2,-3}{
      \name{0}{r}\mcode{(for (i $\infty$) (move r $\epsilon$) (move $\epsilon$ $\epsilon$))}
    }{circle\\\exampleFunction{figures/logoTasks/logo51}{figures/logoTasks/logo63_dilated}}
    \vinvention{pu}{circle}{
      \noArguments{1}\mcode{(pen-up (move 1 0))}
    }{pick up pen\\and move}
    \vinvention{repeated}{pu}{
      \name{2}{n$,$d$,$a}\mcode{(for (i n) (move d a))}
    }{repeated segment\\\exampleFunction{figures/logoTasks/logoDemo1_dilated}{figures/logoTasks/logoDemo0_dilated.png}}
    \hinvention{square}{circle}{
      \name{3}{d}\mcode{(\use{2} 4 d (/ $2\pi$ 4))}
    }{square\\\exampleFunction{figures/logoTasks/logo139_dilated}{figures/logoTasks/logo142_dilated}}
    \vinvention{smooth}{square}{
      \name{4}{d$,$a}\mcode{(\use{2} $\infty$ d a)}
    }{Smooth curve\\\exampleFunction{figures/logoTasks/logoDemo2_dilated}{figures/logoTasks/logoDemo3_dilated}}
    \vinvention{angle}{smooth}{
      \name{5}{n}\mcode{(/ $2\pi$ n)}
    }{$\frac{2\pi}{n}$}
    \hinvention{semi}{square}{
      \noArguments{6}\mcode{(\use{4} $\epsilon$ $\epsilon$)}
    }{semicircle\\\exampleFunction{figures/logoTasks/logo55_dilated}{figures/logoTasks/logo62_dilated}}
    \vinvention{snow}{semi}{
      \name{7}{n$,$f}\mcode{(for (i n) (move 0 (\use{5} n)) (get/set f))}
    }{rotational symmetry\\\exampleFunction{figures/logoTasks/logo119_dilated}{figures/logoTasks/logo68_dilated}}
    \vinvention{line}{snow}{
      \noArguments{8}\mcode{(move 1 0)}
    }{line segment}

    \draw[->] (t1.south) -- (square.north);
    \draw[->] (t2.south) -- (circle.north);
    \draw[->] (t3.south) -- (semi.north);
    \draw[->] (t2.south) -- (snow.west);
    \draw[->] (t2.south) -- (pu.east);
    \draw[->] (t3.south) to[out=320,in=45] (line.east);
    \draw[->] (t3.south) to[out=200,in=120] (snow.west);

    \draw[->] (snow.west) -- (angle.east);
    \draw[->] (smooth.west) -- (repeated.east);
    \draw[->] (semi.west) -- (smooth.east);
    \draw[->] (square.west) -- (repeated.east);
  \end{tikzpicture}

  \end{figure}
